A brief comparison of speed of Interior Point and EM algorithms

### 2016-12-07 analysis/IPvsEM.Rmd
I hid (long) output when knitting IPvsEM.Rmd.

```{r model_fitting}
df = data.frame()
cat("method --optmethod-- sim\n")
for(method in c("fdr","shrink")) {
  for(optmethod in c("mixIP","cxxMixSquarem")) {
    df = rbind(df,data.frame(method = method,optmethod = optmethod,
           timed_sims(list(method = method,optmethod = optmethod),
                           nsim = 50,nmin = 10,nmax = 1e5)))
  }
}
cat("\n")

# Summarize the results in a table.
cat("Average computation time (in seconds):\n")
print(as.table(by(df,df[c("method","optmethod")],
                  function (x) mean(x$elapsed.time))))
```

>>>>

```{r model_fitting, results='hide'}
df = data.frame()
cat("method --optmethod-- sim\n")
for(method in c("fdr","shrink")) {
  for(optmethod in c("mixIP","cxxMixSquarem")) {
    df = rbind(df,data.frame(method = method,optmethod = optmethod,
           timed_sims(list(method = method,optmethod = optmethod),
                           nsim = 50,nmin = 10,nmax = 1e5)))
  }
}
cat("\n")
```

Summarize the model fitting results in a table.

```{r model_fitting_summary}
cat("Average computation time (in seconds):\n")
print(as.table(by(df,df[c("method","optmethod")],
                  function (x) mean(x$elapsed.time))))
```
